. See: \url{http://www.acm.org/about/class/1998/} for help using the ACM
Classification system.

\section{Introduction}\label{introduction}

Maybe one paragraph (previous years talk about motivation in similar
work in intro and have one-two paragraphs in a background/related work
section) about how previous work tried to come up with frameworks to
support writers and tried to investigate the writers problems. They
describe the motivation and the need for such a system: * Tracking
Changes in Collaborative Writing: Edits, Visibility and Group
Maintenance Old examples: * Quilt: A collaborative tool for cooperative
writing - 1988 * User-centred iterative design of collaborative software
-1993 * what do co-authors use? * They try to find relevant changes: *
Flexible Diff-ing in a collaborative writing system * What did they do?
Deriving High-Level edit histories in Wikis

newer examples also try to classify changes: * How a Structured Document
Model Can Support Awareness in Collaborative Authoring * A framework for
asynchronous change awareness in collaborative documents and workspaces
* some try to find conflicts (different definition of conflict though):
* Enabling truly collaborative writing on a computer * and some try to
find an explicit structur in texts: * A narrative-based collaborative
writing tool for constructing coherent technical documents * trying to
predict: * WikiChanges - Exposing Wikipedia Revision Activity

When authors collaborate to write a paper, they need to communicate
constantly to ensure that they are all on the same page. Because the
authors need to make sure that their edits are coherent with the rest of
the paper, including sections written by others, they need to read the
entire paper frequently, or rely on updates communicated by their
coauthors. Even with constant communication, authors can get lost in the
volume of edits from other collaborators. Therefore, an assistive system
with a summary of the significant changes contributed by other authors
would be helpful. We hypothesize that when an author makes a significant
edit to a paragraph, it eventually triggers a series of adjustments in
related paragraphs. Before these adjustments occur, semantic conflicts
might occur between authors. We wanted a collaborative writing system to
also predict when and where these conflicts may occur, in order to alert
even more specifically.

The system is composed of the following three components: (1) tracking
paragraphs; (2) identifying significant changes to paragraphs, and (3)
predicting future changes to the article. Tracking paragraphs through
paper revisions is a core capability required for monitoring changes and
predicting them. The identification of significant content changes is
important for a system to understand how important different changes are
and whether collaborating authors should be notified. Predicting future
changes enables the system to not only report to authors about changes
that have already been made, but also draw their attention to other
parts of the document that might require changes as a result of the
changes made.

INSERT THIS SOMEHOW IN MOTIVATION {[}A significant edit demanded changes
in related paragraphs eighty percent of the time{]}, but in
collaborative writing, these resulting edits do not occur
instantaneously. Instead of waiting for other authors to discover the
inconsistency caused by one author's edit, we want an assistive system
that can alert relevant authors about paragraphs that might need an
additional look as a result of an edit.

\section{Approach}\label{approach}

\subsection{Data}\label{data}

The described research is based on the revision history from a wide
variety of Wikipedia articles that undergo intense editing processes.
Wikipedia is a unique source because it presents extensive data for
collaborative writing. The findings use the complete revision revision
history of 41 different articles chosen from a diverse set of topics,
from famous people and places to mathematical algorithms to novels. The
revision histories were downloaded as raw xml data. We removed
Wikipedia-specific tags that indicate formatting and other irrelevant
data, and eliminated versions of the articles under 150 characters, as
they did not contain enough information. To focus only on revisions with
consequential changes, the versions with simple typo fixes{[}1{]} were
eliminated as well. This resulted in a total of 17,199 versions across
the 41 articles, with an average length of 25.71 paragraphs. Wikipedia
data affords results applicable to other collaborative writing spaces,
because although the average article has over 400 contributing authors,
most of these authors make a one-time change. In fact, on average, 15
authors make 80\% of the edits to an article. This enables the
consideration of interactions between authors, which is crucial for
learning about collaborative behavior.

\subsection{Tracking paragraphs}\label{tracking-paragraphs}

We developed a novel mapping algorithm that uses the Levenshtein edit
ratio measure, which is defined in equation 1.

This method differed from previous attempts in the sense that it tracks
paragraphs as a whole instead of just the longest common subsequence as
used in {[}a b c{]} or on a sentence level as used in {[}a b c{]}.

A Levenshtein ratio close to one between two paragraphs indicates a high
similarity between them, while a ratio close to zero indicates the
opposite. For each revision, we computed the Levenshtein ratio between
each paragraph in the old version and each paragraph in the new version.
Two paragraphs are mapped across the revision if they each had the
highest Levenshtein ratio for the other. If a paragraph in the new
version had no ``matches'', meaning that none of its ratios were above a
threshold of 0.4, this paragraph was new. If a paragraph in the old
version had no ``matches'', then it was deleted in the revision. The
image below demonstrates this algorithm: paragraphs 9, 10 and 12 of the
old version were deleted, while the others found clear matches.

\subsection{Detect Significant
Changes}\label{detect-significant-changes}

We define a significant change as a noticeable change in the paragraph's
topic and content. For this calculation, the Levenshtein ratio does not
provide the right kind of information. For example, if two of the
paragraph's sentences switch places, the Levenshtein ratio would
decrease despite no meaningful change in content. On the other hand,
changing a couple key words will slightly lower the Levenshtein ratio,
but could drastically affect the content.

As shown in figure 1, which shows the distribution of the differences
between a paragraph's Levenshtein ratios and LSI ratios, the Levenshtein
and LSI ratios demonstrate very different statistics. {[}INSERT
FIGURE{]}

Therefore, we use a topic modeling approach, which is a better fit for
assessing changes in content. Latent Semantic Indexing is a form of
topic modeling that calculates the topic similarity between two texts.
Its strengths lie in accounting for synonyms and not penalizing for
typographical errors. The process begins by composing a corpus for each
Wikipedia article from all of the documents (paragraphs of the versions
of the article). It analyzes tokens (a specific instance of a word),
eliminating those that only occur once, as well as stopword tokens, such
as `the' or `and'. It then creates a TF-IDF matrix, which assigns a
weight to every token in each document, which indicates the importance
of that token for this document. This weight increases proportionally to
the frequency of the word in the document, but accounts for the
frequency of the word in the corpus, such that the frequent occurrence
of a usually uncommon word is given a larger weight to signify this
importance.

The latent semantic indexing method then reduces the dimensions of the
matrix, clustering synonyms, words with similar topics, and words that
usually occur together. When comparing two paragraphs, the method
computes the cosine similarity between each paragraph's row vector.
Paragraphs that have similar topics will have a large cosine similarity
value.

By calculating the topic similarity between two concurrent versions of
an edited paragraph, the system can detect whether a significant change
has occurred. If the cosine similarity between the two paragraphs was
below an empirically determined threshold of 0.8, we label the edit as
significant.

\subsection{Predicting Future
Conflicts}\label{predicting-future-conflicts}

We hypothesized that a paragraph that underwent a significant change
would cause inconsistencies in related paragraphs, prompting edits.
Therefore, in order to predict future conflicts, an assistive system
needs to detect significant changes and then determine consequently
which paragraphs were most likely to change.

We looked at three possible types of inter-paragraph relationships.
Paragraphs could be related by physical proximity: perhaps the
neighboring paragraphs would require adjustments, as they are likely
part of the same section. Paragraphs could also be related by topic. For
example, in an academic paper, the discussion section and the conclusion
should present similar themes. If one changes, the other may need to be
edited to reflect this change. For each significant change, we used the
existing LSI Topic Model to determine which paragraphs discussed similar
topics. Lastly, paragraphs could be related because of similar edit
histories. For each significant change, we evaluated the edit history of
this paragraph with every other paragraph in the article. We labeled
pairs as related if they changed or remained unchanged together over
half the time. With a higher threshold, the sample size decreases, but
with a lower threshold, the results become less predictive of a
significant change prompting further edits. This threshold strikes a
balance between these two outcomes.

To evaluate these both of these suspected relationships, we looked at
the related paragraphs' edit patterns in the ten versions following the
significant change. If the related paragraphs changed together over half
the time, the paragraphs with this relationship proved to be related in
the future, verifying the relationship at the time of the significant
change.

\section{Findings}\label{findings}

\subsection{Tracking Paragraphs}\label{tracking-paragraphs-1}

To evaluate the method for tracking paragraphs through consecutive
versions of a paper, we calculated the number of versions from the
paragraphs' inception to its demise. On average, paragraphs lasted 83
article revisions.

\subsection{Detecting Significant
Changes}\label{detecting-significant-changes}

Using the LSI Topic Similarity model and a threshold ratio of 0.8, we
labeled about 15

We evaluated a random sample of these edits to determine that this
method successfully classifies edits. We provide an example of a
significant edit below. While these paragraphs are clearly the same, the
edit is significant because it contributes content and changes the tone
of the paragraph.

OLD: After complaints arose during the renovation in the late 1980s of
the early residential colleges, a swing dormitory was built in 1998 to
facilitate housing students during the massive overhaul of buildings
that had seen only intermediate improvements in plumbing, heating,
electrical and network wiring, and general maintenance over their
35-to-80-year existence. The new Residence Hall is not a residential
college, but houses students from other colleges during renovations. It
is commonly called ``Swing Space'' by the students; it's official name
``Boyd Hall'' is unused. ---------------------------------------------
NEW: In 1990, Yale launched a series of massive overhauls to the older
residential buildings, whose decades of existence had seen only routine
maintenance and incremental improvements to plumbing, heating, and
electrical and network wiring. Calhoun College was the first to see
renovation. Various unwieldy schemes were used to house displaced
students during the yearlong projects, but complaints finally moved Yale
to build a new residence hall between the gym and the power plant. It is
commonly called ``Swing Space'' by the students; its official name
``Boyd Hall'' is unused.

\subsection{Predicting Future
Conflicts}\label{predicting-future-conflicts-1}

We evaluated various inter-paragraph relationships to determine which
paragraphs are more likely to require editing after a significant change
occurs in the article. As seen in figure {[}X{]}, when a paragraph is
edited for the first time in a while, further adjustments are triggered
in the near future.

Caption: After a significant change at version 0, consequent edits are
more frequent.

We looked at two measures that indicate that a paragraph may need
attention. First, the related paragraphs experience at least one
significant change within the next ten versions, indicating that a
semantic discrepancy was introduced and required fixing. Second, and
more importantly, the related paragraphs relationship was correctly
predicted; that is, they are still related ten versions after the
significant change, meaning that they change together (or remain
unchanged together) more than half the time. This is a stronger
indication than just undergoing at least one significant change.

With respect to the first measure, the relationships of edit history and
topic similarity are much more predictive than physical proximity, as
shown in table {[}X{]}. They are also significantly more predictive than
random sample controls. For controls, we compare with the original
paragraph as well as a random sample of any ten consecutive versions
within Wikipedia article histories.

Relationship or Control Percentage of times that paragraph experienced
at least one significant change Edit History 81 Topic Similarity .
Physical Proximity 24 Paragraph with original significant change 40
Random Sample of Paragraphs 15

More importantly, with respect to the second measure, we correctly
predicted 63

Relationship Number Found Successfully Linked Ratio of Successfully
Linked Topic Similarity 1,869 1,203 63 Editing History 27,722 19,685 71

Lastly, to ensure independence from specific articles, we calculated the
correlation between our statistics across all of our Wikipedia articles.
The correlation coefficient was 0.99 for all numbers.

\section{Discussion}\label{discussion}

As demonstrated by the long average lifespan of a paragraph, our
algorithm for tracking paragraphs throughout versions of an article is
capable of following paragraphs through complex edits. This provides the
basis for detecting significant changes and anticipating future semantic
conflicts. Our edit evaluation method successfully detects the most
significant changes using the LSI Topic Similarity model. Based on these
significant changes, we anticipate possible semantic conflicts in linked
paragraphs. After a significant change, paragraphs related to the edited
paragraph were indeed more likely to be edited in response a couple
versions later. Paragraphs linked by similar edit histories were most
likely to need editing, with paragraphs linked by topic similarity not
far behind.

In the future, we can build an assistive system that uses our methods to
improve the collaborative writing environment. The paragraph tracking
algorithm makes it possible to create a list of authors who have
contributed to a specific paragraph, which is crucial for determining
who to alert when significant edits occur. By labeling edits as
significant, the system can save authors time, since they will no longer
need to discern which of their peers' edits actually matter. Then, when
a significant edit occurs, the system can alert authors to related
paragraphs that will likely need adjusting, allowing authors to fix
semantic conflicts immediately, instead of discovering them later.

We imagine a couple other helpful components for an assistive system
that our methods could provide the foundation for. Using text summary
algorithms, the system could provide a succinct textual summary of
significant changes already detected. The system could also \ldots{}.

\section{Conclusion}\label{conclusion}

Both of these measures of relatedness are successful in determining
whether a paragraph will change together in the future. Consequently, we
assert that if significant edit occurs, related paragraphs should also
be edited. A proposed assistive system will alert the relevant authors
of related paragraphs if this resulting edit does not occur. By
detecting relationships between paragraphs in a multi-authored paper,
our system can predict and alert appropriate authors if a significant
change has the potential to create a semantic conflict within the paper.
